\textbf{ANALYSIS OF \\ MACHINE LEARNING \\ APPLIED TO BOARD GAMES}

### 2022-11-27 doc/workplan.tex

\newpage
\noindent
We will expand our knowledge of machine learning and implement everything in C++.
Different algorithms and neural networks will be assigned throughout the group depending on individual wishes. \\\\
Since all of us are interested in programming and the topic, we constantly work on the project.
It is therefore neither fully necessary nor helpful to assign strict deadlines.
Bertil Lundell, teacher in programming, checks on our progress every other week in order to keep our process going.
We intend to be finished with 2 to 3 different neural networks until the 2nd December when half of the work should be submitted. \\\\
\textbf{Preliminary work distribution:} \\\\
Jonathan Hallström: Deep Q-learning \\\\
Adam Amanbaev: Convolutional Neural Network / Heuristic Algorithms \\\\
Hugo Åkerfeldt: Heuristical Algorithms \\\\
Romeo Patzer: Heuristic Algorithms \\\\
Alvar Edvardsson: Deep Q-learning

>>>>

\newpage
\noindent
We will expand our knowledge of machine learning and implement everything in C++.
Different algorithms and neural networks will be assigned throughout the group depending on individual wishes. \\\\
Since all of us are interested in programming and the topic, we constantly work on the project.
It is therefore neither fully necessary nor helpful to assign strict deadlines.
Bertil Lundell, teacher in programming, checks on our progress every other week in order to keep our process going.
We intend to be finished with 2 to 3 different neural networks until the 2nd December when half of the work should be submitted. \\\\
\textbf{Preliminary work distribution:} \\\\
Hugo Åkerfeldt: Heuristical Algorithms \\\\
Alvar Edvardsson: Deep Q-learning 
Jonathan Hallström: Deep Q-learning \\\\
Adam Amanbaev: Convolutional Neural Network / Heuristic Algorithms \\\\
Romeo Patzer: Heuristic Algorithms \\\\
